Stochastic Convolutional Sparse Coding \\ Supplementary Material

### 2019-08-19 VMV19/supplement.tex
add directory

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\usepackage{array}
\usepackage{epstopdf}
\usepackage{cuted}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{3722} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\input{macro}
\begin{document}

%%%%%%%%% TITLE
\title{Stochastic Convolutional Sparse Coding \\ Supplementary Material}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle

\section{Solvers for LASSO and QCQP}
Algorithm~\ref{algo:ADMMLasso} is used to optimize a LASSO problem in the following form:
\begin{equation}
    \minimize{\code} \frac{1}{2}\|\signal - \Filter \code \|_2^2 + \lambda\| \code \|_1
\end{equation}

@@

\begin{figure*}[h]
\centering
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchFruit100.pdf}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideFruit100.pdf}
  \end{subfigure}
\caption{Zoom-in view of the filters from Fig.~1 of the main manuscript.}
\end{figure*}

\section{Zooming in on the Filters}

Here we zoom in on the filters from Fig.~1 in the main manuscript. Notice that our filters look more smooth for those Gabor-like filters and also contains less number of noise-like filters.

\section{Additional Experiments}
In order to show the robustness of the proposed algorithms, We also conduct experiments on city dataset. We first compare SBCSC with the state-of-the-art batch-mode algorithm, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}. Similar to the results shown in Fig.~1 in the main manuscript, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm with better outcomes and runtime performance. Since the learning is performed on handful datasets, both of them learn quite a few data-specific image features. These data-specific image features have the shortage of the generalization ability, which can be revealed in the image inpainting application. For example, the eighth image, which contains a large portion of the texture information existed in the filters learned from city dataset, can be significantly better reconstructed by such filters compared to using those learned from fruit dataset. However, it may exhibit poorer performance on other types of images.

\begin{figure*}[h]
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobj-city.pdf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobj-city.pdf}
\end{subfigure}

\centering
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/batchCity100.pdf}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/heideCity100.pdf}
\end{subfigure}
\vspace{0.2cm}

    \resizebox{0.8\linewidth}{!}{
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
            \cline{1-11}
            Image & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
            \hline
            PSNR~[10] & 29.67 & \textbf{28.14} & 29.58 & 29.69 & 28.74 & 29.43 & 27.89  & 30.13 & 27.03 & 30.61 \\
            \hline
            PSNR ours & \textbf{29.78} & \textbf{28.14} & \textbf{29.67}  & \textbf{29.85} & \textbf{28.88} & \textbf{29.95} & \textbf{27.97} & \textbf{30.37} & \textbf{27.14} & \textbf{30.89} \\
            \hline
        \end{tabular} }

\caption{Experimental results obtained on the city dataset. Top: Convergence comparison between the-state-of-art batch method and SBCSC with different subsampling probability. Middle: Learned filters by SBCSC with $p=0.1$ and the comparable method. Even though these dictionaries look similar, our method learns more smooth filters. Compared to the learned filters in Fig.~1 of the main manuscript, they have different representations of the dictionaries, where data-specific features are learned from handful training images. Bottom: Numerical comparisons of the reconstruction quality obtained by the presented filters in the image inpainting application.}
\label{fig:subsampleResult-city}
\end{figure*}

@@

\section{Over-complete Dictionary and Large Datasets}
\begin{figure*}[h]
\centering
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
\end{subfigure}

\caption{Experimental results obtained on city dataset. Left: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach. Right: Testing PSNR with respect to execution time.}
\label{fig:onlineSmall-city}
\end{figure*}

\begin{figure*}[h]
\centering
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/nonZeroElement.pdf}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
  \includegraphics[width=1\linewidth]{figure/reconPSNR.pdf}
\end{subfigure}

\caption{Left: number of non-zero elements in the codes for different images ($10 ~ 256 \times 256$ images). Right: PSNR between the reconstructed images and the original ones.}
\label{fig:overVSunder}
\end{figure*}

@@

In this section, we first show the improved sparse representation of the natural images with over-complete dictionaries ($K=400$) over under-complete ones ($K=100$). The numerical comparisons of number of non-zero elements and its corresponding reconstruction PSNR for various images are shown in Fig.~\ref{fig:overVSunder}. Here, we define the non-zero elements as the codes whose coefficient is no less than $0.1$. We could observe that at all times, using over-complete dictionary leads to a sparser representation of the images, roughly $8\%-10\%$ reduction on the non-zero elements. Meanwhile, it achieves dramatically improved reconstruction quality, over $1$ dB on average.

We then verify the importance of a large dataset when learning the over-complete dictionary. in Fig.~\ref{fig:overCompleteDic-dataset}, we show a visual and quantitative comparisons between the over-complete dictionaries respectively learned by batch-mode algorithm on small dataset (the fruit dataset) and online-mode algorithm on large dataset (1000 images). Most of the filters learned from small dataset have poor structures and reveal very limited representative ability. The numerical results also demonstrate that it even shows a degraded reconstruction performance compared to the under-complete dictionary. Owing to plentiful training samples, our over-complete dictionary not only shows visually decent structures and more representative image features, but also leads to a significant improvement on image reconstruction. Based on all experimental results, it implies that the number of filters and number of training samples are both essential in the CSC model, therefore, the proposed algorithm has prominent advantages over the existing approaches.

@@

% --- DO NOT DELETE ---
% Local Variables:
% mode: latex
% mode: flyspell
% mode: TeX-PDF
% End:

>>>>

% ---------------------------------------------------------------------------
% Author guideline and sample document for EG publication using LaTeX2e input
% D.Fellner, v1.15, Dec 14, 2018

\documentclass{egpubl}
\usepackage{EGVMV19}

% --- for  Annual CONFERENCE
% \ConferenceSubmission   % uncomment for Conference submission
% \ConferencePaper        % uncomment for (final) Conference Paper
% \STAR                   % uncomment for STAR contribution
% \Tutorial               % uncomment for Tutorial contribution
% \ShortPresentation      % uncomment for (final) Short Conference Presentation
% \Areas                  % uncomment for Areas contribution
% \MedicalPrize           % uncomment for Medical Prize contribution
% \Education              % uncomment for Education contribution
% \Poster                 % uncomment for Poster contribution
% \DC                     % uncomment for Doctoral Consortium
%
% --- for  CGF Journal
% \JournalSubmission    % uncomment for submission to Computer Graphics Forum
% \JournalPaper         % uncomment for final version of Journal Paper
%
% --- for  CGF Journal: special issue
% \SpecialIssueSubmission    % uncomment for submission to , special issue
% \SpecialIssuePaper         % uncomment for final version of Computer Graphics Forum, special issue
%                          % EuroVis, SGP, Rendering, PG
% --- for  EG Workshop Proceedings
 \WsSubmission      % uncomment for submission to EG Workshop
% \WsPaper           % uncomment for final version of EG Workshop contribution
% \WsSubmissionJoint % for joint events, for example ICAT-EGVE
% \WsPaperJoint      % for joint events, for example ICAT-EGVE
% \Expressive        % for SBIM, CAe, NPAR
% \DigitalHeritagePaper
% \PaperL2P          % for events EG only asks for License to Publish

% --- for EuroVis
% for full papers use \SpecialIssuePaper
% \STAREurovis   % for EuroVis additional material
% \EuroVisPoster % for EuroVis additional material
% \EuroVisShort  % for EuroVis additional material

% !! *please* don't change anything above
% !! unless you REALLY know what you are doing
% ------------------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage{dfadobe}

\usepackage{cite}  % comment out for biblatex with backend=biber
% ---------------------------
%\biberVersion
\BibtexOrBiblatex
%\usepackage[backend=biber,bibstyle=EG,citestyle=alphabetic,backref=true]{biblatex}
%\addbibresource{egbibsample.bib}
% ---------------------------
\electronicVersion
\PrintedOrElectronic
% for including postscript figures
% mind: package option 'draft' will replace PS figure by a filename within a frame
\ifpdf \usepackage[pdftex]{graphicx} \pdfcompresslevel=9
\else \usepackage[dvips]{graphicx} \fi

\usepackage{egweblnk}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\usepackage{array}
\usepackage{epstopdf}
\usepackage{cuted}
\input{macro}
% ---------------------------------------------------------------------
% end of prologue

% EG author guidelines plus sample file for EG publication using LaTeX2e input
% D.Fellner, v2.03, Dec 14, 2018

\title{Stochastic Convolutional Sparse Coding \\
        Supplementary Material}

% for anonymous conference submission please enter your SUBMISSION ID
% instead of the author's name (and leave the affiliation blank) !!
% for final version: please provide your *own* ORCID in the brackets following \orcid; see https://orcid.org/ for more details.
\author{Submission ID: 1010}
%\author[D. Fellner \& S. Behnke]
%{\parbox{\textwidth}{\centering D.\,W. Fellner\thanks{Chairman Eurographics Publications Board}$^{1,2}$\orcid{0000-0001-7756-0901}
%        and S. Behnke$^{2}$\orcid{0000-0001-5923-423X}
%%        S. Spencer$^2$\thanks{Chairman Siggraph Publications Board}
%        }
%        \\
%% For Computer Graphics Forum: Please use the abbreviation of your first name.
%{\parbox{\textwidth}{\centering $^1$TU Darmstadt \& Fraunhofer IGD, Germany\\
%         $^2$Graz University of Technology, Institute of Computer Graphics and Knowledge Visualization, Austria
%%        $^2$ Another Department to illustrate the use in papers from authors
%%             with different affiliations
%       }
%}
%}
% ------------------------------------------------------------------------

% if the Editors-in-Chief have given you the data, you may uncomment
% the following five lines and insert it here
%
% \volume{36}   % the volume in which the issue will be published;
% \issue{1}     % the issue number of the publication
% \pStartPage{1}      % set starting page

%-------------------------------------------------------------------------
\begin{document}

% uncomment for using teaser
% \teaser{
%  \includegraphics[width=\linewidth]{eg_new}
%  \centering
%   \caption{New EG Logo}
% \label{fig:teaser}
%}

\maketitle
%-------------------------------------------------------------------------
\section{Solvers for LASSO and QCQP}
Algorithm~\ref{algo:ADMMLasso} is used to optimize a LASSO problem in the following form:
\begin{equation}
    \minimize{\code} \frac{1}{2}\|\signal - \Filter \code \|_2^2 + \lambda\| \code \|_1
\end{equation}

@@

\section{Additional Experiments}

\begin{figure}[h]
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/iteVSobj-city.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/timeVSobj-city.pdf}
\end{subfigure}

\caption{Experimental results obtained on the city dataset. Convergence comparison between the-state-of-art batch method and SBCSC with different subsampling probability.}
\label{fig:subsampleResult-city}
\end{figure}

In order to show the robustness of the proposed algorithms, We also conduct experiments on city dataset. We first compare SBCSC with the state-of-the-art batch-mode algorithm, and the results are shown in Fig.\ \ref{fig:subsampleResult-city}. Similar to the results shown in Fig.~1 in the main manuscript, SBCSC, with $p=0.1$, outperforms the compared batch-mode algorithm in terms of runtime performance.

\begin{figure}[h]
\centering
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-ite.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=1\linewidth]{figure/onlineVSliu-time.pdf}
\end{subfigure}

\caption{Experimental results obtained on city dataset. Top: Convergence of the test set objectives for our method (SOCSC) and the state-of-the-art online approach. Bottom: Testing PSNR with respect to execution time.}
\label{fig:onlineSmall-city}
\end{figure}

@@

@@

\section{Over-complete Dictionary and Large Datasets}

We verify the importance of a large dataset when learning the over-complete dictionary. in Fig.~\ref{fig:overCompleteDic-dataset}, we show a visual and quantitative comparisons between the over-complete dictionaries respectively learned by batch-mode algorithm on small dataset (the fruit dataset) and online-mode algorithm on large dataset (1000 images). Most of the filters learned from small dataset have poor structures and reveal very limited representative ability. The numerical results also demonstrate that it even shows a degraded reconstruction performance compared to the under-complete dictionary. Owing to plentiful training samples, our over-complete dictionary not only shows visually decent structures and more representative image features, but also leads to a significant improvement on image reconstruction. Based on all experimental results, it implies that the number of filters and number of training samples are both essential in the CSC model, therefore, the proposed algorithm has prominent advantages over the existing approaches.

@@
